Unifying Lower Bounds on Prediction Dimension of Consistent Convex Surrogates

### 2021-05-27 cvx-flats-neurips21/cvx-flats.tex
Forgot to save; small changes

%\citet[Corollary 10]{agarwal2015consistent} provide a necessary condition for the direct convex elicitation of single-valued properties, yielding bounds via the dimensionality of level sets.
Consistency is often the desired notion of corresponding to a prediction task since it is a prerequisite for deriving ERM bounds, but is often studied through the equivalent or necessary conditions of calibration, indirect elicitation, or embedding; notions of prediction dimension have been studied for surrogates satisfying each of the criteria.
\citet{ramaswamy2016convex} introduce \emph{convex calibration dimension} for problems in Quadrant 1 to study the prediction dimension of convex calibrated losses; in Q1, this is precisely equal to convex consistency dimension of a target loss.

>>>>

%\citet[Corollary 10]{agarwal2015consistent} provide a necessary condition for the direct convex elicitation of single-valued properties, yielding bounds via the dimensionality of level sets.
Consistency is often the desired notion of corresponding to a prediction task since it is a prerequisite for deriving ERM bounds, but is often studied through the equivalent or necessary conditions of calibration, indirect elicitation, or embedding; notions of prediction dimension have been studied for surrogates satisfying each of the criteria.
\citet{ramaswamy2016convex} introduce \emph{convex calibration dimension} and some lower bonuds for problems in Quadrant 1 to study the prediction dimension of convex calibrated losses; in Q1, this is precisely equal to convex consistency dimension of a target loss.
